\documentclass{article}

\begin{document}

\title{SSL/TLS Certificate Setup Script README}
\author{Your Name}
\date{\today}

\maketitle

\section{Introduction}

This document provides instructions and information for using the SSL/TLS Certificate Setup Script. The script is designed to automate the process of setting up a Certificate Authority (CA) and configuring SSL/TLS certificates for secure communication in a multi-machine environment.

\section{Prerequisites}

Before using the script, ensure the following prerequisites are met:

\begin{itemize}
    \item Both the CA server and client server must have SSH access enabled.
    \item You should have sudo privileges on both machines.
\end{itemize}

\section{Usage}

To use the script, follow these steps:

\begin{enumerate}
    \item Clone this repository and navigate to the script's directory.
    
    \item Modify the \texttt{folder\_names} array to specify the directories you want to create on the CA server.

    \item Execute the script, and it will perform the following tasks:

    \begin{itemize}
        \item Create the main CA folder on the CA server.
        \item Create specified folders within the CA directory.
        \item Generate a self-signed CA certificate on the CA server.
        \item Generate a certificate signing request (CSR) on the client server.
        \item Transfer the CSR to the CA server.
        \item Move the CSR to the CA's request folder.
        \item Copy the private key to the CA's private folder.
        \item Use the CA to sign the client's certificate.
        \item Transfer the signed certificate and CA certificate to the client server.
        \item Configure Apache to accept SSL/TLS connections on the client server.
    \end{itemize}
\end{enumerate}

\section{Notes}

\begin{itemize}
    \item This script is provided as a template and should be adapted to your specific environment and requirements.
    \item Ensure that you have a secure SSH connection and proper authentication.
    \item Review and customize the script for security and compliance with your organization's policies.
\end{itemize}

\end{document}
